Hydra Battles and Cie

### 2021-08-19 doc/part-hydras.tex
conversion to Alectryon (chapter 4, to be continued)

\label{instance-epsilon0}
\begin{Coqsrc}
Instance Epsilon0 : ON Lt compare.  
(* ... *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Instance Epsilon0_correct :
  ON_correct epsilon0 Epsilon0 (fun alpha => inject (cnf alpha)).
\end{Coqsrc}

@@

    \begin{Coqsrc}
    Definition SubON_same_op  `{OA : @ON A ltA  compareA}
           `{OB : @ON B ltB  compareB}
           {iota : A -> B} 
           {alpha: B}
           {_ : SubON OA OB alpha iota}
           (f : A -> A -> A)
           (g : B -> B -> B)
      :=
      forall x y,  iota (f x y) = g (iota x) (iota y).
    \end{Coqsrc}

@@

    \begin{Coqsrc}
    Fixpoint oplus (alpha beta : T1) : T1 :=
      let fix oplus_aux beta {struct beta} :=
          match alpha, beta with
            | zero, _ => beta
            | _,  zero => alpha
            | ocons a1 n1 b1, ocons a2 n2 b2 =>
              match compare a1 a2 with
                |  Gt => ocons a1 n1 (oplus b1 beta)
                |  Lt => ocons a2 n2 (oplus_aux b2)
                |  Eq => ocons a1 (S (n1 + n2)%nat) (oplus b1 b2)
              end
          end
      in oplus_aux beta.

    Infix "o+" := oplus  (at level 50, left associativity).
    \end{Coqsrc}

@@

    \begin{Coqsrc}
    Lemma oplus_alpha_0 (alpha : T1) : alpha o+ zero = alpha.
    Proof.
      destruct alpha; reflexivity.
    Qed.

    Lemma oplus_0_beta (beta : T1): zero o+ beta = beta.
    Proof.
      destruct beta; reflexivity.
    Qed.
    \end{Coqsrc}

>>>>

\input{movies/snippets/E0/InstanceEpsilon0}

\label{instance-epsilon0}

@@

\input{movies/snippets/Correctness_E0/injectDef}

@@

\input{movies/snippets/ON_Generic/SubONSameOp}

@@

    \input{movies/snippets/Hessenberg/oplusDef}

@@

    \input{movies/snippets/Hessenberg/oplusNeutral}
